Model Comparison

### 2020-02-11 stats/model_comparison.Rmd
add model comparison and test run fully bayesian model

## Dummy example for MH

```{r}
# Model prediction files are very large - can't put them on github as is 
# files below contain the two iterations for each model (1286 & 7185)

# load model predicitons
test_prag <- readRDS("../saves/test_prag.rds")

test_global <- readRDS("../saves/test_global.rds")

test_flat <- readRDS("../saves/test_flat.rds")

bind_rows(
  test_prag, 
  test_global, 
  test_flat
)%>%
  spread(model, pred)%>%
  right_join(d_model_comp)%>%
  mutate(log_like_prag = log(ifelse(correct == 1, pragmatic, 1 - pragmatic)),
         log_like_global = log(ifelse(correct == 1, global, 1 - global)),
         log_like_flat = log(ifelse(correct == 1, flat, 1 - flat)))%>%
  mutate(prag_vs_global = log_like_prag - log_like_global, # subtract likelihood for each predictions and model
         prag_vs_flat= log_like_prag - log_like_flat,
         global_vs_flat = log_like_global - log_like_flat) %>%
  summarise(prag_vs_global = sum(prag_vs_global), # sum up likelihood difference to get log Bayes factor
            prag_vs_flat = sum(prag_vs_flat),
            global_vs_flat = sum(global_vs_flat))%>%
  gather(model, logBF)

>>>>

```{r}

d_model_comp.summarized <- d_model_comp %>% 
  group_by(alignment, item, age) %>% 
  summarize(n=n(), k = sum(correct))

# join predictions with the data

model_comp <- bind_rows(

  readRDS("../saves/model_pred_prag.rds") %>%
    right_join(d_model_comp.summarized) %>%
    select(model,chain,iteration, age, alignment,item,pred, n, k),

  readRDS("../saves/model_pred_global.rds") %>%
    right_join(d_model_comp.summarized)%>%
    select(model,chain,iteration, age, alignment,item,pred, n, k),

   readRDS("../saves/model_pred_flat.rds") %>%
    right_join(d_model_comp.summarized)%>%
    select(model,chain,iteration, age, alignment,item,pred, n, k),

  readRDS("../saves/model_pred_prior.rds") %>%
    right_join(d_model_comp.summarized)%>%
    select(model,chain,iteration, age, alignment,item,pred, n, k)
) %>%
  mutate(
    log_like = dbinom(x = k, size = n, prob = pred, log = TRUE)
  ) %>%
  group_by(chain, model, iteration) %>%
  summarize(total_likelihood_sample = sum(log_like)) %>%
  group_by(chain, model) %>%
  summarize(marginal_likelihood = matrixStats::logSumExp(total_likelihood_sample)) %>%
  spread(model, marginal_likelihood)%>%
  mutate(prag_vs_global = pragmatic - global, # subtract likelihood for each predictions and model
         prag_vs_flat= pragmatic - flat,
         prag_vs_prior= pragmatic - prior,
         global_vs_flat = global - flat,
         global_vs_prior = global - prior,
         flat_vs_prior = flat - prior) %>%
  select(-pragmatic, -global, -flat, - prior) %>%
  gather(model, logBF, -chain)
